Verifying Demonstrations

### 2017-08-27 conclusions.tex
Edits conclusion

\begin{frame}<presentation>
  \begin{remark}
    \begin{itemize}
      \item All current methods lack most of verifiability.
      \item Some provide universal verifiability (V\ref{UniversalVerif}).

        \pause

      \item Most cannot estimate the correct participation count.
    \end{itemize}
  \end{remark}
\end{frame}

>>>>

\begin{frame}<presentation>
  \begin{block}{Verifiability}
    \begin{itemize}
      \item All current methods lack most of verifiability.
      \item Some can provide universal verifiability.
    \end{itemize}
  \end{block}

  \pause{}

  \begin{block}{Correctness}
    \begin{itemize}
      \item Most cannot estimate the correct participation count.
      \item Some can (theoretically) give an upper bound.
    \end{itemize}
  \end{block}
\end{frame}

\subsection{Open problems}

\begin{frame}
  \frametitle{Sybil}
  \begin{question}
    How to solve Sybil, can we piggyback on existing \acp{PKI}?
    E.g.\ through~\cite{Cinderella}.
  \end{question}

  \begin{question}
    Can we otherwise bind identifiable keys to unique ring signature keys?
  \end{question}

  \begin{question}
    This is similar to the double-spending problem for cryptocurrencies, can 
    we reuse any such techniques?
    (Not like in Bitcoin, but more like ecash~\cite{ecash} and the like.)
  \end{question}
\end{frame}

\begin{frame}
  \frametitle{Distributed systems}
  \begin{question}
    \begin{itemize}
      \item Malicious nodes want to provide Alice with a view that her proof is 
        included.
      \item Everyone else is provided a view without Alice.
      \item How can we ensure a consistent view for everyone?
    \end{itemize}
  \end{question}

  \begin{question}
    How can we do blockchain branch and merge?
    That is needed to recover from the above attack.
  \end{question}
\end{frame}

\begin{frame}
  \frametitle{Anonymous communication}
  \begin{question}
    How do we submit the proofs to storage?
  \end{question}

  \mode<presentation>{%
    \begin{remark}
      \begin{itemize}
        \item Without anonymous submission we don't get proof privacy, thus no 
          receipt freeness either.
        \item Voting normally uses mix-nets.
        \item Submit over Tor~\cite{Tor}?
      \end{itemize}
    \end{remark}
  }
\end{frame}
